title

### 2013-02-04 paper.tex
Added to introduction

In response to the potential of water shortages in the United States
by 2025, we present a series of recommended infrastructure developments
intended to most efficiently meet future demands. We first create
a projection of future water supply and demand at the county level
based on extrapolating past data collected by the US Geological Survey,
providing a visualization of water needs across the country. Based
on these projections, and geographical data concerning the location
of each county, we determine that a water management strategy primarily
based on the construction of a pipeline network is ideal. We model
counties as vertices and pipelines as edges in order to employ a minimum
spanning tree algorithm to determine the optimal placement of new
pipelines in order to minimize costs. Anticipating the possibility
of funding being less than that required to construct all recommended
infrastructure, we create a priority ordering of the pipelines, using
a utility function based on county population data. We also consider
the water supply of the country as a whole, providing recommendations
as to the number of de-salinization plants required to meet the change
in demand.

@@

@@

We begin our paper with a projection of the likely levels of water
supply (given no additional interference) and demand in the United
States by 2025 on a county-by-county basis. Our primary source of
data is the County-level water use data made publically available
by the US Geological Survey (USGS) in years 1985, 1990, 1995, 2000,
and 2005 \cite{key-2,key-3,key-4,key-5,key-6}. Using our projected
figures, we describe a means of minimizing the expected cost of constructing
water storage and water purification systems using a network flow
algorithm.

@@

\subsection{Total Supply}

@@

As a result, we firmly recommend that the entirety of our proprosed
infrastructure developments, particularly the national pipeline network,
be implemented over the upcoming years.
\begin{thebibliography}{10}
\bibitem{key-1}Cai, X., Cline, S., Rosegrant, M. (2002). Global Water
Outlook to 2025. \emph{International Food Policy Research Institute.}

>>>>

In response to the potential of water shortages in the United States
by 2025, we present a series of recommended infrastructure developments
intended to most efficiently meet future demands. We first create
a projection of future water usage at the county level
based on extrapolating past data collected by the US Geological Survey,
providing a visualization of water needs across the country. Based
on these projections, and geographical data concerning the location
of each county, we determine that a water management strategy primarily
based on the construction of a national pipeline network is ideal. We model
counties as vertices and pipelines as edges in order to employ a minimum
spanning tree algorithm to determine the optimal placement of new
pipelines in order to minimize costs and redundancy. Anticipating the possibility of funding being less than that required to construct all recommended
infrastructure, we create a priority ordering of the pipelines, using
a utility function based on county population data. We also consider
the water supply of the country as a whole, providing recommendations
as to the number of de-salinization plants and reservoirs to be built to meet the change in demand.

@@

Our overall conclusions are as follows:
\begin{enumerate}
\item The US will not see a drastic increase in water usage. We estimate in Section \ref{total} that the overall increase in water usage by 2025 will not exceed 2 \%. In fact many regions will see a net decrease in water usage, according to our models.
\item In the absence of overall water usage growth, our water management plan focuses on being robust to short-term crises like droughts. To solve the latter we propose a national grid of high-volume pipelines to improve connectivity and transport water to areas with increased seasonal water needs.
\item Second, using cluster analysis we identify areas in which the growth in water demand will be most severe and recommend specific infrastructure in these regions to balance increased demand.
\item Finally, we make recommendations on how to improve sustainability and decrease environmental impact, especially pollution and the depletion of groundwater.
\end{enumerate}

@@

We begin our paper with a projection of the likely levels of water
demand in the United States by 2025 on a county-by-county basis. Our primary source of data is the County-level water use data made publically available
by the US Geological Survey (USGS) in years 1985, 1990, 1995, 2000,
and 2005 \cite{key-2,key-3,key-4,key-5,key-6}. Using our projected
figures, we describe a means of minimizing the expected cost of constructing
water storage and water purification systems using a network flows
algorithm.

@@

\subsection{Total Supply\label{total}}

@@

As a result, we firmly recommend that the entirety of our proprosed
infrastructure developments, particularly the national pipeline network,
be implemented over the upcoming years.
\begin{thebibliography}{10}
\bibitem[1]{key-1}Cai, X., Cline, S., Rosegrant, M. (2002). Global Water
Outlook to 2025. \emph{International Food Policy Research Institute.}
